%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Web Developer} % Job title
    {Freelance} % Organization
    {Toronto, ON} % Location
    {May 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working with Amnesty International Canada in revamping their Youth Activists website.}
        \item {Provided consultations to organization staff members over Skype.}
        \item {Designed, developed and presented website mockups focusing on needs of the organization and ensuring strong UI/UX.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Urgent Action Digital Coordinator} % Job title
    {Amnesty International Canada} % Organization
    {Toronto, ON} % Location
    {Nov. 2016 - May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked in partnership with the Urgent Action Coordinator to format and dispatch urgent human rights cases and actions across Canada.}
        \item {Redesigned the Urgent Action website within a Drupal template using CSS and self-created graphics. }
        \item {Developed and published Urgent Actions on the SOS Amnesty iOS app to over a thousand users per push.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Youth Intern} % Job title
    {Amnesty International Canada} % Organization
    {Ottawa, ON} % Location
    {Sep. 2015 - Dec. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Ensured maintenance of members database and executed search queries to produce reports.}
        \item {Presented to multiple high school classes discussing Amnesty International, human rights, and human rights activism.}
        \item {Provided outreach and support to secondary and post-secondary schoolteachers and students across Canada involved or interested in the Amnesty Youth and Student Program.}
      \end{cvitems}
    }
    
    %---------------------------------------------------------
  \cventry
    {Policy and Programs Assistant } % Job title
    {Ontario Ministry of Transportation } % Organization
    {Toronto, ON} % Location
    {May 2015 – Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Supported policy advisors of the provincial Road User Safety team in vehicle policy, program planning, delivery, and evaluation.}
        \item {Reviewed driver program curricula of various public and private Ontario organizations to ensure compliance with curriculum standards of the Ontario Ministry of Transportation.}
      \end{cvitems}
    }
  
%---------------------------------------------------------
\end{cventries}
