%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Web Developer} % Job title
    {Freelance} % Organization
    {Toronto, ON} % Location
    {May 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing a custom Wordpress child theme and website for Amnesty International Canada's Youth Program using PHP, JavaScript, jQuery, HTML and CSS.}
        \item {Provided consultations to organization staff members over Skype.}
        \item {Designed, developed and presented website mockups focusing on needs of the organization and ensuring strong UI/UX.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Urgent Action Digital Coordinator} % Job title
    {Amnesty International Canada} % Organization
    {Toronto, ON} % Location
    {Nov. 2016 - May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked in partnership with the Urgent Action Coordinator to format and dispatch hundreds of urgent human rights cases and actions across Canada.}
        \item {Developed and published Urgent Actions on the SOS Amnesty iOS app to over a thousand users per push.}
        \item {Redesigned the Urgent Action website running on Drupal using CSS and self-created graphics. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Youth Intern} % Job title
    {Amnesty International Canada} % Organization
    {Ottawa, ON} % Location
    {Sep. 2015 - Dec. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Provided outreach and support to secondary and post-secondary schoolteachers and students across Canada involved or interested in the Amnesty Youth and Student Program.}
		\item {Presented to multiple high school classes discussing Amnesty International, human rights, and human rights activism.}
        \item {Ensured maintenance of members database and executed search queries to produce reports.}
      \end{cvitems}
    }
    
    %---------------------------------------------------------
  \cventry
    {Policy and Programs Assistant } % Job title
    {Ontario Ministry of Transportation } % Organization
    {Toronto, ON} % Location
    {May 2015 – Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Supported policy advisors of the provincial Road User Safety team in vehicle policy, program planning, delivery, and evaluation.}
        \item {Reviewed driver program curricula of provincial organizations to ensure compliance with curriculum standards of the ministry.}
      \end{cvitems}
    }
    
    %---------------------------------------------------------
  \cventry
    {Proctor } % Job title
    {Department of Psychology, University Of Toronto } % Organization
    {Toronto, ON} % Location
    {September 2014 – May 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Invigilated course examinations under the Department of Psychology, ensuring the adherence to the University of Toronto's academic integrity guidelines. }
      \end{cvitems}
    }
    %---------------------------------------------------------
  \cventry
    {Research and Program Assistant} % Job title
    {New College} % Organization
    {Toronto, ON} % Location
    {May 2014 – Aug. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided research and general program assistance for two undergraduate programs: New College’s Community Engaged Learning program, and the first year foundations program, New One: Learning Without Borders.}
        \item {Contributed administrative support, web page updating, publicity and communication, research of scholarly literature, social data compilation and analysis. }
      \end{cvitems}
    }
    
  
%---------------------------------------------------------
\end{cventries}
